Assessing paravascular transport in the parenchyma by PDE constrained optimization.

### 2018-10-22 tex/paper.tex
update

>>>>

Previous studies~\cite{holter2017interstitial, smith2017glymphatic} suggest that diffusion dominates in the interstitium. Furthermore, 
~\cite{asgari2016glymphatic, brynjfm, diem?} have found that dissipation in the paravascular spaces adds less than a factor two
to diffusion for solute transportation. If we take into account then that the vasculature occupy 3-5\% of the volume
of the brain and the paravascular space presumably occupy less space, then the factor 30\% (?) that we find here 
seems significant and it is difficult to explain or ignore.
